### 2019-10-21 2019_neurips_kr2ml/model.tex
KR2ML - start
work in progress - experiments
work on experiments, changed figure placement

\begin{wrapfigure}{r}{0.80\textwidth}
	\centering
	\includegraphics[width=0.78\textwidth]{../img/architecture/samnet_architecture4}
	\caption{General architecture of SAMNet}
	\label{fig:samnet}
\end{wrapfigure}

%\begin{figure}[hbtp]
%	\centering
%	\includegraphics[width=0.7\textwidth]{../img/architecture/samnet_architecture4}
%	\caption{General architecture of SAMNet}
%	\label{fig:samnet}
%\end{figure}

SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}).
The model makes a single pass over the frames in temporal order, accessing one frame at a time.
The memory locations store relevant objects representing contextual information about words in text and visual objects extracted from video. 
Each location of the memory stores a $d$-dimensional vector. %, where $d$ is a global parameter.
The memory can be accessed through either content-based addressing, via dot-product attention, or location-based addressing. 
Using gating mechanisms, correct objects can be retrieved 
in order to perform multi-step spatio-temporal reasoning over text and video.  
%A notable feature of this design is that the number of addresses $N$ can be set to different values during training and 
%testing to fit the characteristics of data.

\begin{wrapfigure}{r}{0.8\textwidth}
	\centering
	\includegraphics[width=0.78\textwidth]{../img/architecture/samcell_reasoning}
	\caption{Unfolded reasoning steps with operations performed by the SAMCell}
	\label{fig:samcell}
\end{wrapfigure}

%\begin{figure}[hbtp]
%	\centering
%	\includegraphics[width=0.7\textwidth]{../img/architecture/samcell_reasoning}
%	\caption{Single reasoning step in SAMCell}
%	\label{fig:samcell}
%\end{figure}

@@

For details of the modules not covered here, please see the appendix.

>>>>

\begin{figure}[b!]
	\centering
	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
	\caption{General architecture of SAMNet}
	\label{fig:samnet}
\end{figure}

SAM Network (SAMNet for short) is an end-to-end differentiable recurrent model equipped with an external memory~(\cref{fig:samnet}).
At the conceptual level SAMNet draws from two core ideas:
compositional reasoning as proposed e.g. in MAC (Memory-Attention-Composition) Network~\cite{hudson2018compositional,marois2018transfer}
and utilization of external memory in Memory-Augmented Neural Networks such as NTM (Neural Turing Machine)~\cite{graves2014neural}, DNC (Differentiable Neural Computer)~\cite{graves2016hybrid} or DWM (Differentiable Working Memory)~\cite{jayram2018learning}.

A distinctive feature of the SAM Network is that it makes a single pass over the frames in temporal order, accessing one frame at a time.
The memory locations store relevant objects representing contextual information about words in text and visual objects extracted from video. 
Each location of the memory stores a $d$-dimensional vector. %, where $d$ is a global parameter.
The memory can be accessed through either content-based addressing, via dot-product attention, or location-based addressing. 
Using gating mechanisms, correct objects can be retrieved 
in order to perform multi-step spatio-temporal reasoning over text and video.  
A notable feature of this design is that the number of addresses $N$ can be set to different values during training and testing to fit the characteristics of data.

\begin{figure}[t!]
	\centering
	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
	\caption{Unfolded reasoning steps with operations performed by the SAMCell}
	\label{fig:samcell}
\end{figure}

@@

%For details of the modules not covered here, please see the appendix.

### 2019-10-21 2019_neurips_vigil/appendix_model.tex

We illustrate the key reasoning steps taken by the model with the following example.
Let the question be: ``Does color of u now equal the color of the latest circle?''
and let the frames be as shown in~\cref{fig:frame-seq}.
The answer is true in the last frame because the latest circle can be found in Frame 2. 
\begin{figure}[!h]
\begin{minipage}{0.25\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 1"}
\label{fig:frame-1}
\end{minipage}\hfill
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 2"}
	\label{fig:frame-1}
\end{minipage}\hfill
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 3"}
	\label{fig:frame-1}
\end{minipage}\hfill
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 4"}
		\label{fig:frame-1}
\end{minipage}
\caption{Sample sequence of input frames} 
\label{fig:frame-seq}
\end{figure}

SAMNet gives the correct answer for this example and we can interpret its reasoning process via a movie that we can generate.
The key steps in that reasoning process are shown below. Working backwards, the following shows what happens in the key steps
of the reasoning process.
In Step 1 of processing Frame 4 (see~\cref{fig:frame-4-step-1}), we see that the object representing the letter u is where the attention 
is, both in text and in image. We also see that the temporal classifier gives the highest weight to the context ``now''.
\begin{figure}[!h]
\centering
  \includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 4 Step 1"}
\caption{State of SAMNet in a particular reasoning step} 
\label{fig:frame-4-step-1}
\end{figure}

Now there is no circle in this frame even though it is a valid candidate . This is detected by SAMNet,
as shown in~\cref{fig:frame-4-step-6}. Even though the textual attention is on the right word
and the temporal classification is ``latest'', there
is no valid visual attention.
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 4 Step 6"}
	\caption{State of SAMNet in a particular reasoning step} 
	\label{fig:frame-4-step-6}
\end{figure}

But in Step 6 of processing Frame 2 (see~\cref{fig:frame-2-step-6}), 
we see that the object representing the circle is where the attention is.
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{"../img/visualization/sample 2/Frame 2 Step 6"}
	\caption{State of SAMNet in a particular reasoning step} 
	\label{fig:frame-2-step-6}
\end{figure}
Moreover, the ``Add New`` gate value is high enough that the valid object representing
the visual encoding of the circle is stored in memory. Note that this is not perfect:
this value should have been close to 1 but the model is still able to use it for 
correct prediction.

>>>>

We illustrate the key reasoning steps taken by the model with the following example.
Let the question be: ``Does color of u now equal the color of the latest circle?''
and let the frames be as shown in~\cref{fig:frame-seq}.
The answer is true in the last frame because the latest circle can be found in Frame 2. 
\begin{figure}[!h]
\begin{minipage}{0.25\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 1"}
\label{fig:frame-1}
\end{minipage}\hfill
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2"}
	\label{fig:frame-1}
\end{minipage}\hfill
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 3"}
	\label{fig:frame-1}
\end{minipage}\hfill
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4"}
		\label{fig:frame-1}
\end{minipage}
\caption{Sample sequence of input frames} 
\label{fig:frame-seq}
\end{figure}

SAMNet gives the correct answer for this example and we can interpret its reasoning process via a movie that we can generate.
The key steps in that reasoning process are shown below. Working backwards, the following shows what happens in the key steps
of the reasoning process.
In Step 1 of processing Frame 4 (see~\cref{fig:frame-4-step-1}), we see that the object representing the letter u is where the attention 
is, both in text and in image. We also see that the temporal classifier gives the highest weight to the context ``now''.
\begin{figure}[!h]
\centering
  \includegraphics[width=\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4 Step 1"}
\caption{State of SAMNet in a particular reasoning step} 
\label{fig:frame-4-step-1}
\end{figure}

Now there is no circle in this frame even though it is a valid candidate . This is detected by SAMNet,
as shown in~\cref{fig:frame-4-step-6}. Even though the textual attention is on the right word
and the temporal classification is ``latest'', there
is no valid visual attention.
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4 Step 6"}
	\caption{State of SAMNet in a particular reasoning step} 
	\label{fig:frame-4-step-6}
\end{figure}

But in Step 6 of processing Frame 2 (see~\cref{fig:frame-2-step-6}), 
we see that the object representing the circle is where the attention is.
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2 Step 6"}
	\caption{State of SAMNet in a particular reasoning step} 
	\label{fig:frame-2-step-6}
\end{figure}
Moreover, the ``Add New`` gate value is high enough that the valid object representing
the visual encoding of the circle is stored in memory. Note that this is not perfect:
this value should have been close to 1 but the model is still able to use it for 
correct prediction.

### 2019-10-21 2019_neurips_vigil/experiments.tex

\begin{figure}[htbp]
	\centering
  \begin{subfigure}{\textwidth}
    \includegraphics[width=0.92\textwidth]{results/samnet_cog_orig_canonical_no_labels.png}
  \end{subfigure}%
  \newline
  \begin{subfigure}{\textwidth}
	\includegraphics[width=0.93\textwidth]{results/samnet_cog_orig_hard.png}
  \end{subfigure}%
\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the COG model (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
\label{fig:samnet_cog_detailed}
\end{figure}

\begin{wrapfigure}{r}{0.45\textwidth}
	\centering
	\includegraphics[width=0.45\textwidth]{results/samnet_cog_overall_transfer.png}
	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
	\label{fig:samnet_cog_overall_transfer}
\end{wrapfigure}

>>>>

\begin{figure}[htbp]
	\centering
  \begin{subfigure}{\textwidth}
    \includegraphics[width=0.92\textwidth]{../results/samnet_cog_orig_canonical_no_labels.png}
  \end{subfigure}%
  \newline
  \begin{subfigure}{\textwidth}
	\includegraphics[width=0.93\textwidth]{../results/samnet_cog_orig_hard.png}
  \end{subfigure}%
\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the COG model (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
\label{fig:samnet_cog_detailed}
\end{figure}

\begin{wrapfigure}{r}{0.45\textwidth}
	\centering
	\includegraphics[width=0.45\textwidth]{../results/samnet_cog_overall_transfer.png}
	\caption{Total accuracies of SAMNet (blue) and COG models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
	\label{fig:samnet_cog_overall_transfer}
\end{wrapfigure}
